Turbulence in compact to giant HII regions

### 2022-09-01 strucfunc_paper.tex
Add in the new figure of surface brightness fluctuations

\newcommand\vexp{\ensuremath{v_{\text{exp}}}}
An alternative interpretation,
as discussed in \citep{2011MNRAS.413..705L},
is that \(\sigma\los\) includes a contribution due to
ordered large-scale velocity gradients
(for instance, radial expansion)
in addition to the turbulence,
whereas \(\sigma\pos\) includes only the turbulent motions. 
% Constant v_exp : sig_los = sqrt(sig_pos**2 + v_exp**2)
Assuming a constant value \vexp{} for the ordered contribution,
one would predict \(\sigma\los = (\sigma\pos^2 + \vexp^2)^{1/2}\),
which is shown by the dot-dashed line in Figure~\ref{fig:los-vs-pos}
for the case \(\vexp \approx \SI{8}{km.s^{-1}}\).
It can seen that such a relationship reproduces the 
observationally derived values equally as well as the linear fit.
On the other hand, we can rule out the possibility that
\vexp{} might increase in proportion to the turbulent velocity dispersion
since that would predict that \(\sigma\los \propto \sigma\pos\),
which is inconsistent with the observations as discussed above.

However, as pointed out by \citet{arthur2016turbulence},
the previous analysis is oversimplified since the presence
of density fluctuations (or, more generally, emissivity fluctuations)
means that the plane-of-sky dispersion of centroids is also affected
by ordered large-scale velocity gradients along the line of sight.
These leads to a third potential explanation of the
\(\sigma\pos\)--\(\sigma\los\) relationship.
In the limit that the direct effects of velocity fluctuations are
negligible, the prediction is that \(\sigma\pos / \sigma\los \approx \)

As for the interpretation, it is possible to consider that large fluctuations of the turbulent velocities, which are spread over the entire ionized extent of the nebula, increase monotonically with the plane-of-sky dispersion.
In this scenario, the main broadening mechanisms causing kinematical disorder along the line-of-sight are related to the velocity gradients of the clumpiness in the cloud and turbulent movements.
On the plane-of-sky the consequences of those gradients and movements are measured in every pixel, consequently the spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
Thus the \(\sigma\pos\) and \(\langle \sigma_{\text{los}} \rangle\) parameters increase in the same amount as the fluctuations grows \citep{2011MNRAS.413..705L}.

>>>>

\newcommand\vexp{\ensuremath{v_{\text{exp}}}}
An alternative interpretation,
as discussed in \citet{2011MNRAS.413..705L},
is that \(\sigma\los\) includes a contribution due to
ordered large-scale velocity gradients
(for instance, radial expansion)
in addition to the turbulence,
whereas \(\sigma\pos\) includes only the turbulent motions. 
% Constant v_exp : sig_los = sqrt(sig_pos**2 + v_exp**2)
Assuming a constant value \vexp{} for the ordered contribution,
one would predict \(\sigma\los = (\sigma\pos^2 + \vexp^2)^{1/2}\),
which is shown by the dot-dashed line in Figure~\ref{fig:los-vs-pos}
for the case \(\vexp \approx \SI{8}{km.s^{-1}}\).
It can seen that such a relationship reproduces the 
observationally derived values equally as well as the linear fit.
On the other hand, we can rule out the possibility that
\vexp{} might increase in proportion to the turbulent velocity dispersion
since that would predict that \(\sigma\los \propto \sigma\pos\),
which is inconsistent with the observations as discussed above.

However, as pointed out by \citet{arthur2016turbulence},
the previous analysis is oversimplified since the presence
of density fluctuations (or, more generally, emissivity fluctuations)
means that the plane-of-sky dispersion of centroids \(\sigma\pos\)
is \emph{not} independent of the 
ordered large-scale velocity gradients along the line of sight.
This leads to a third potential explanation of the
\(\sigma\pos\)--\(\sigma\los\) relationship.
In the limit that the direct contribution of
turbulent velocity fluctuations to \(\sigma\pos\) is negligible,
the prediction is that \(\sigma\pos / \sigma\los \approx \sigma_{E/E_0}\)
where \( \sigma_{E/E_0} = \langle \delta E^2 \rangle^{1/2} / E_0\) is the RMS fractional
variation in emissivity \(\delta E\) (on scales \(\ge r_0\))
with respect to the mean emissivity \(E_0\).

\begin{figure}
\centering 
\includegraphics[width=\linewidth]{Figures/bright-hist-multi}
\caption{
  Panels a--g show histograms (blue) of the probability density function (PDF)
  of the \ha{} surface brightness of \hii{} regions in our sample.
  Smooth lines (orange) show fitted log-normal distributions.
  Surface brightness maps were rebinned by averaging
  into pixels of size \(0.5 r_0\) before calculating the PDF to suppress
  fluctuations at scales smaller than the correlation length.
  Panel h plots the ratio of velocity dispersions (see Figure~\ref{fig:los-vs-pos})
  against the RMS fractional brightness fluctuations calculated from the PDFs.
}
\label{fig:brightness-pdfs}
\end{figure}

In order to empirically disentangle the relative importance
of these three mechanisms, we require high quality measurements
of a much larger sample of \hii{} regions
than have so far been obtained.
In the meantime
is most important

We therefore have an embarrassment of 
As for the interpretation, it is possible to consider that large fluctuations of the turbulent velocities, which are spread over the entire ionized extent of the nebula, increase monotonically with the plane-of-sky dispersion.
In this scenario, the main broadening mechanisms causing kinematical disorder along the line-of-sight are related to the velocity gradients of the clumpiness in the cloud and turbulent movements.
On the plane-of-sky the consequences of those gradients and movements are measured in every pixel, consequently the spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
Thus the \(\sigma\pos\) and \(\langle \sigma_{\text{los}} \rangle\) parameters increase in the same amount as the fluctuations grows \citep{2011MNRAS.413..705L}.
